NoTCP: steganographic tricks to bypass middleboxes

### 2014-07-14 paper/paper.tex
cleaned up references

\vspace{-4mm}
\begin{align*}
Checksum_2 & = Checksum_1 - header_1 + header_2 \\
Checksum_i & = Checksum_{i-1} - header_{i-1} + header_i \\
 ... \\
Checksum_n & = Checksum_1 - header_1 + header_n
\end{align*}

@@

\vspace{-4mm}
\begin{align*}
Checksum_{target} & = Opcode + header_1 \\
Checksum_n = Opcode_C & = Opcode + header_n
\end{align*}

@@

After the first data packets there are potential problems with segment splitting and coalescing : control stream may reach the destination in the middle of a payload of a packet and would be impossible to find without scanning the whole payload. Either SCTP style chunking or MPTCP DSS option can be reused to get around the problem. The obvious drawback of such choice is that control stream becomes subject to flow control. We leave refinement of the full control channel for future work.

@@

% \clearpage
%Only show things we really cite :)
% \nocite{*}
{

>>>>

% \vspace{-2mm}
\begin{align*}
Checksum_2 & = Checksum_1 - header_1 + header_2 \\
Checksum_i & = Checksum_{i-1} - header_{i-1} + header_i \\
 ... \\
Checksum_n & = Checksum_1 - header_1 + header_n
\end{align*}

@@

% \vspace{-2mm}
\begin{align*}
Checksum_{target} & = Opcode + header_1 \\
Checksum_n = Opcode_C & = Opcode + header_n
\end{align*}

@@

The focus of our work is to show the possibility of exchanging control information within the packet header. We therefore leave refinement of the full control channel for future work.

@@

\clearpage
%Only show things we really cite :)
% \nocite{*}
{
